---
output:
  pdf_document: default
  html_document: default
---

### Preparation

Run this cell to clear the variables in your global R environment.

```{r}
rm(list = ls())
ls()
```

## Libraries

```{r}
library(caret)
library(RWeka)
library(dplyr)
library(caTools)
library(randomForest)
```


## Define basics
```{r}
# Drop Src.ipaddr && Dest.ipaddr && start,end time && mac
drops <- c("srcIP",  "dstIP","srcMac", "dstMac", "timeFirst", "timeLast",
          "srcIPCC", "dstIPCC", "srcIPOrg", "dstIPOrg", "srcMac_dstMac_numP", "dstPortClass", "srcMacLbl_dstMacLbl", "ethVlanID",
          "hdrDesc",
          "vlanID",
          "icmpBFTypH_TypL_Code", "ipOptCnt", "ipOptCpCl_Num",
          "macPairs", "ip6OptCntHH_D", "ip6OptHH_D", "tcpWinSzThRt", "icmpEchoSuccRatio")
set.seed(1003)

```


## Data file process function
```{r}
load_data <- function(data) {
  data.noVPN <- get(paste(data, "noVPN", sep = "."))
  data.1111 <- get(paste(data, "1111", sep = "."))
  
  data.noVPN <- data.noVPN[, !(names(data.noVPN) %in% drops)]
  data.1111 <- data.1111[, !(names(data.1111) %in% drops)]
  
  data.noVPN$isVPN <- 0
  data.1111$isVPN <- 1
  
  data.noVPN = data.frame(data.noVPN)
  data.1111 = data.frame(data.1111)
  data.data <- rbind(data.1111,data.noVPN)
  
  assign(paste(data, "noVPN", sep = "."), data.noVPN, envir = globalenv())
  assign(paste(data, "1111", sep = "."), data.1111, envir = globalenv())
  assign(paste(data, "data", sep = "."), data.data, envir = globalenv())
}
```


```{r}
# Remain data in lab
slack.lab.10.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab10re_flows.csv")
slack.lab.10.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab10_1111_flows.csv")
slack.lab.1.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab1_flows.csv")
slack.lab.1.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab1_1111_flows.csv")
slack.lab.3.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab3_flows.csv")
slack.lab.3.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab3_1111_flows.csv")
slack.lab.6.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab6_flows.csv")
slack.lab.6.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab6_1111_flows.csv")
slack.lab.8.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab8_flows.csv")
slack.lab.8.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab8_1111_flows.csv")


# Data in residence
slack.res.10.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes11_flows.csv")
slack.res.10.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes10_1111_flows.csv")
slack.res.1.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes1_flows.csv")
slack.res.1.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes1_1111_flows.csv")
slack.res.3.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes3_flows.csv")
slack.res.3.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes3_1111_flows.csv")
slack.res.6.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes6_flows.csv")
slack.res.6.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes6_1111_flows.csv")
slack.res.8.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes8_flows.csv")
slack.res.8.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes8_1111_flows.csv")

```

```{r}
load_data("slack.lab.10")
load_data("slack.lab.1")
load_data("slack.lab.3")
load_data("slack.lab.6")
load_data("slack.lab.8")

load_data("slack.res.10")
load_data("slack.res.1")
load_data("slack.res.3")
load_data("slack.res.6")
load_data("slack.res.8")

slack.lab.noVPN <- rbind(slack.lab.10.noVPN,slack.lab.1.noVPN,slack.lab.3.noVPN,
                        slack.lab.6.noVPN,slack.lab.8.noVPN)
slack.lab.1111 <- rbind(slack.lab.10.1111,slack.lab.1.1111,slack.lab.3.1111,
                        slack.lab.6.1111,slack.lab.8.1111)

slack.res.noVPN <- rbind(slack.res.10.noVPN,slack.res.1.noVPN,slack.res.3.noVPN,
                          slack.res.6.noVPN,slack.res.8.noVPN)
slack.res.1111 <- rbind(slack.res.10.1111,slack.res.1.1111,slack.res.3.1111,
                         slack.res.6.1111,slack.res.8.1111)

slack.data.noVPN <- rbind(slack.lab.noVPN,slack.res.noVPN)
slack.data.1111 <- rbind(slack.lab.1111,slack.res.1111)

```


```{r}
twitch.lab.10.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab10_flows.csv")
twitch.lab.1.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab1_flows.csv")
twitch.lab.3.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab3_flows.csv")
twitch.lab.6.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab6_flows.csv")
twitch.lab.8.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab8_flows.csv")

twitch.lab.10.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab10_1111_flows.csv")
twitch.lab.1.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab1_1111_flows.csv")
twitch.lab.3.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab3_1111_flows.csv")
twitch.lab.6.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab6_1111_flows.csv")
twitch.lab.8.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab8_1111_flows.csv")

twitch.res.10.noVPN = read.csv("t2/streaming/none/res/streamingCapRes10_flows.csv")
twitch.res.1.noVPN = read.csv("t2/streaming/none/res/streamingCapRes1_flows.csv")
twitch.res.3.noVPN = read.csv("t2/streaming/none/res/streamingCapRes3_flows.csv")
twitch.res.6.noVPN = read.csv("t2/streaming/none/res/streamingCapRes6_flows.csv")
twitch.res.8.noVPN = read.csv("t2/streaming/none/res/streamingCapRes8_flows.csv")

twitch.res.10.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes10_1111_flows.csv")
twitch.res.1.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes1_1111_flows.csv")
twitch.res.3.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes3_1111_flows.csv")
twitch.res.6.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes6_1111_flows.csv")
twitch.res.8.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes8_1111_flows.csv")
```


## Clean data - define cols to drop
```{r}
load_data("twitch.lab.10")
load_data("twitch.lab.1")
load_data("twitch.lab.3")
load_data("twitch.lab.6")
load_data("twitch.lab.8")

load_data("twitch.res.10")
load_data("twitch.res.1")
load_data("twitch.res.3")
load_data("twitch.res.6")
load_data("twitch.res.8")

twitch.lab.noVPN <- rbind(twitch.lab.10.noVPN,twitch.lab.1.noVPN,twitch.lab.3.noVPN,
                        twitch.lab.6.noVPN,twitch.lab.8.noVPN)
twitch.lab.1111 <- rbind(twitch.lab.10.1111,twitch.lab.1.1111,twitch.lab.3.1111,
                        twitch.lab.6.1111,twitch.lab.8.1111)

twitch.res.noVPN <- rbind(twitch.res.10.noVPN,twitch.res.1.noVPN,twitch.res.3.noVPN,
                          twitch.res.6.noVPN,twitch.res.8.noVPN)
twitch.res.1111 <- rbind(twitch.res.10.1111,twitch.res.1.1111,twitch.res.3.1111,
                         twitch.res.6.1111,twitch.res.8.1111)

twitch.data.noVPN <- rbind(twitch.lab.noVPN,twitch.res.noVPN)
twitch.data.1111 <- rbind(twitch.lab.1111,twitch.res.1111)

```


```{r}
browsing.lab.10.noVPN = read.csv("t2/browsing/none/lab/browsingCapLab10_flows.csv")
browsing.lab.1.noVPN = read.csv("t2/browsing/none/lab/browsingCapLab1_flows.csv")
browsing.lab.3.noVPN = read.csv("t2/browsing/none/lab/browsingCapLab3_flows.csv")
browsing.lab.6.noVPN = read.csv("t2/browsing/none/lab/browsingCapLab6_flows.csv")
browsing.lab.8.noVPN = read.csv("t2/browsing/none/lab/browsingCapLab8_flows.csv")

browsing.lab.10.1111 = read.csv("t2/browsing/1.1.1.1/lab/browsingCapLab10_1111_flows.csv")
browsing.lab.1.1111 = read.csv("t2/browsing/1.1.1.1/lab/browsingCapLab1_1111_flows.csv")
browsing.lab.3.1111 = read.csv("t2/browsing/1.1.1.1/lab/browsingCapLab3_1111_flows.csv")
browsing.lab.6.1111 = read.csv("t2/browsing/1.1.1.1/lab/browsingCapLab6_1111_flows.csv")
browsing.lab.8.1111 = read.csv("t2/browsing/1.1.1.1/lab/browsingCapLab8_1111_flows.csv")

browsing.res.10.noVPN = read.csv("t2/browsing/none/res/browsingCapRes10_flows.csv")
browsing.res.1.noVPN = read.csv("t2/browsing/none/res/browsingCapRes1_flows.csv")
browsing.res.3.noVPN = read.csv("t2/browsing/none/res/browsingCapRes3_flows.csv")
browsing.res.6.noVPN = read.csv("t2/browsing/none/res/browsingCapRes6_flows.csv")
browsing.res.8.noVPN = read.csv("t2/browsing/none/res/browsingCapRes8_flows.csv")

browsing.res.10.1111 = read.csv("t2/browsing/1.1.1.1/res/browsingCapRes10_1111_flows.csv")
browsing.res.1.1111 = read.csv("t2/browsing/1.1.1.1/res/browsingCapRes1_1111_flows.csv")
browsing.res.3.1111 = read.csv("t2/browsing/1.1.1.1/res/browsingCapRes3_1111_flows.csv")
browsing.res.6.1111 = read.csv("t2/browsing/1.1.1.1/res/browsingCapRes6_1111_flows.csv")
browsing.res.8.1111 = read.csv("t2/browsing/1.1.1.1/res/browsingCapRes8_1111_flows.csv")
```

## Clean data - define cols to drop
```{r}
load_data("browsing.lab.10")
load_data("browsing.lab.1")
load_data("browsing.lab.3")
load_data("browsing.lab.6")
load_data("browsing.lab.8")

load_data("browsing.res.10")
load_data("browsing.res.1")
load_data("browsing.res.3")
load_data("browsing.res.6")
load_data("browsing.res.8")

browsing.lab.noVPN <- rbind(browsing.lab.10.noVPN,browsing.lab.1.noVPN,browsing.lab.3.noVPN,
                        browsing.lab.6.noVPN,browsing.lab.8.noVPN)
browsing.lab.1111 <- rbind(browsing.lab.10.1111,browsing.lab.1.1111,browsing.lab.3.1111,
                        browsing.lab.6.1111,browsing.lab.8.1111)

browsing.res.noVPN <- rbind(browsing.res.10.noVPN,browsing.res.1.noVPN,browsing.res.3.noVPN,
                          browsing.res.6.noVPN,browsing.res.8.noVPN)
browsing.res.1111 <- rbind(browsing.res.10.1111,browsing.res.1.1111,browsing.res.3.1111,
                         browsing.res.6.1111,browsing.res.8.1111)

browsing.data.noVPN <- rbind(browsing.lab.noVPN,browsing.res.noVPN)
browsing.data.1111 <- rbind(browsing.lab.1111,browsing.res.1111)

```

## Load data files
```{r}
gdrive.lab.10.noVPN = read.csv("t2/gdrive/none/lab/lab10_none_flows.csv")
gdrive.lab.1.noVPN = read.csv("t2/gdrive/none/lab/lab1_none_flows.csv")
gdrive.lab.3.noVPN = read.csv("t2/gdrive/none/lab/lab3_none_flows.csv")
gdrive.lab.6.noVPN = read.csv("t2/gdrive/none/lab/lab6_none_flows.csv")
gdrive.lab.8.noVPN = read.csv("t2/gdrive/none/lab/lab8_none_flows.csv")

gdrive.lab.10.1111 = read.csv("t2/gdrive/1.1.1.1/lab/lab10_1111_flows.csv")
gdrive.lab.1.1111 = read.csv("t2/gdrive/1.1.1.1/lab/lab1_1111_flows.csv")
gdrive.lab.3.1111 = read.csv("t2/gdrive/1.1.1.1/lab/lab3_1111_flows.csv")
gdrive.lab.6.1111 = read.csv("t2/gdrive/1.1.1.1/lab/lab6_1111_flows.csv")
gdrive.lab.8.1111 = read.csv("t2/gdrive/1.1.1.1/lab/lab8_1111_flows.csv")

gdrive.res.10.noVPN = read.csv("t2/gdrive/none/res/res10_none_flows.csv")
gdrive.res.1.noVPN = read.csv("t2/gdrive/none/res/res1_none_flows.csv")
gdrive.res.3.noVPN = read.csv("t2/gdrive/none/res/res3_none_flows.csv")
gdrive.res.6.noVPN = read.csv("t2/gdrive/none/res/res6_none_flows.csv")
gdrive.res.8.noVPN = read.csv("t2/gdrive/none/res/res8_none_flows.csv")

gdrive.res.10.1111 = read.csv("t2/gdrive/1.1.1.1/res/res10_1111_flows.csv")
gdrive.res.1.1111 = read.csv("t2/gdrive/1.1.1.1/res/res1_1111_flows.csv")
gdrive.res.3.1111 = read.csv("t2/gdrive/1.1.1.1/res/res3_1111_flows.csv")
gdrive.res.6.1111 = read.csv("t2/gdrive/1.1.1.1/res/res6_1111_flows.csv")
gdrive.res.8.1111 = read.csv("t2/gdrive/1.1.1.1/res/res8_1111_flows.csv")
```


## Clean data - define cols to drop
```{r}
load_data("gdrive.lab.10")
load_data("gdrive.lab.1")
load_data("gdrive.lab.3")
load_data("gdrive.lab.6")
load_data("gdrive.lab.8")

load_data("gdrive.res.10")
load_data("gdrive.res.1")
load_data("gdrive.res.3")
load_data("gdrive.res.6")
load_data("gdrive.res.8")

gdrive.lab.noVPN <- rbind(gdrive.lab.10.noVPN,gdrive.lab.1.noVPN,gdrive.lab.3.noVPN,
                        gdrive.lab.6.noVPN,gdrive.lab.8.noVPN)
gdrive.lab.1111 <- rbind(gdrive.lab.10.1111,gdrive.lab.1.1111,gdrive.lab.3.1111,
                        gdrive.lab.6.1111,gdrive.lab.8.1111)

gdrive.res.noVPN <- rbind(gdrive.res.10.noVPN,gdrive.res.1.noVPN,gdrive.res.3.noVPN,
                          gdrive.res.6.noVPN,gdrive.res.8.noVPN)
gdrive.res.1111 <- rbind(gdrive.res.10.1111,gdrive.res.1.1111,gdrive.res.3.1111,
                         gdrive.res.6.1111,gdrive.res.8.1111)

gdrive.data.noVPN <- rbind(gdrive.lab.noVPN,gdrive.res.noVPN)
gdrive.data.1111 <- rbind(gdrive.lab.1111,gdrive.res.1111)

```


```{r}
process_data_lab <- function(data) {
  drops <- c("srcIP",  "dstIP","srcMac", "dstMac", "timeFirst", "timeLast",
          "srcIPCC", "dstIPCC", "srcIPOrg", "dstIPOrg", "srcMac_dstMac_numP", "dstPortClass", "srcMacLbl_dstMacLbl", "ethVlanID",
          "hdrDesc",
          "vlanID",
          "icmpBFTypH_TypL_Code")
  apps <- c("slack.lab","twitch.lab","browsing.lab","gdrive.lab")
  others <- apps[ !apps == data]
  other1 <- apps[1]
  other2 <- apps[2]
  other3 <- apps[3]
  
  data.1111 <- get(paste(data, "1111", sep = "."))
  data.1111$isTarget <- 1
  
  other1.1111 <- get(paste(other1, "1111", sep = "."))
  other2.1111 <- get(paste(other2, "1111", sep = "."))
  other3.1111 <- get(paste(other3, "1111", sep = "."))
  data.other.1111 <- rbind(other1.1111,other2.1111,other3.1111)
  data.other.1111$isTarget <- 0
  
  data.all <- rbind(data.other.1111, data.1111)
  s <- data.all %>% select(where(~ n_distinct(.) <= 1))
  drops <- c(drops,colnames(s))
  
  data.other.1111 <- data.other.1111[, !(names(data.other.1111) %in% drops)]
  data.1111 <- data.1111[, !(names(data.1111) %in% drops)]
  
  data.prop = nrow(data.1111)*0.7 / nrow(data.other.1111)
  
  data.other.trnRows  <- sample(nrow(data.other.1111),nrow(data.other.1111)*data.prop)
  data.other.dtrain <- data.other.1111[data.other.trnRows,]
  data.other.dtest  <- data.other.1111[-data.other.trnRows,]

  data.1111.trnRows <- sample(nrow(data.1111),nrow(data.1111)*0.7)
  data.1111.dtrain <- data.1111[ data.1111.trnRows,]
  data.1111.dtest  <- data.1111[-data.1111.trnRows,]

  data.1111.app.dtrain <- rbind(data.other.dtrain,data.1111.dtrain)
  data.1111.app.dtest <- rbind(data.other.dtest,data.1111.dtest)

  data.1111.app.dtrain$isTarget <- as.factor(data.1111.app.dtrain$isTarget)
  data.1111.app.dtest$isTarget <- as.factor(data.1111.app.dtest$isTarget)
  
  assign(paste(data, "dtest", sep = "."), data.1111.app.dtest, envir = globalenv())
  assign(paste(data, "dtrain", sep = "."), data.1111.app.dtrain, envir = globalenv())
  return(drops)
}

```


```{r}
process_data_res <- function(data) {
  apps <- c("slack.res","twitch.res","browsing.res","gdrive.res")
  others <- apps[ !apps == data]
  other1 <- apps[1]
  other2 <- apps[2]
  other3 <- apps[3]
  
  data.1111 <- get(paste(data, "1111", sep = "."))
  data.1111$isTarget <- 1
  
  other1.1111 <- get(paste(other1, "1111", sep = "."))
  other2.1111 <- get(paste(other2, "1111", sep = "."))
  other3.1111 <- get(paste(other3, "1111", sep = "."))
  data.other.1111 <- rbind(other1.1111,other2.1111,other3.1111)
  data.other.1111$isTarget <- 0
  
  data.other.1111 <- data.other.1111[, !(names(data.other.1111) %in% drops)]
  data.1111 <- data.1111[, !(names(data.1111) %in% drops)]
  
  data.prop = nrow(data.1111)*0.7 / nrow(data.other.1111)
  
  data.other.trnRows  <- sample(nrow(data.other.1111),nrow(data.other.1111)*data.prop)
  data.other.dtrain <- data.other.1111[data.other.trnRows,]
  data.other.dtest  <- data.other.1111[-data.other.trnRows,]

  data.1111.trnRows <- sample(nrow(data.1111),nrow(data.1111)*0.7)
  data.1111.dtrain <- data.1111[ data.1111.trnRows,]
  data.1111.dtest  <- data.1111[-data.1111.trnRows,]

  data.1111.app.dtrain <- rbind(data.other.dtrain,data.1111.dtrain)
  data.1111.app.dtest <- rbind(data.other.dtest,data.1111.dtest)

  data.1111.app.dtrain$isTarget <- as.factor(data.1111.app.dtrain$isTarget)
  data.1111.app.dtest$isTarget <- as.factor(data.1111.app.dtest$isTarget)
  
  assign(paste(data, "dtest", sep = "."), data.1111.app.dtest, envir = globalenv())
  assign(paste(data, "dtrain", sep = "."), data.1111.app.dtrain, envir = globalenv())
}

```

```{r}
drops <- process_data_lab("browsing.lab")
browsing.lab.dtrain
browsing.lab.dtest

process_data_res("browsing.res")
browsing.res.dtrain
browsing.res.dtest
```

## C45 - browsing
```{r}
train_control<- trainControl(method="cv", number=10)
browsing.lab.C45Model <- train(isTarget ~., method="J48", data=browsing.lab.dtrain,
                tuneLength = 5,
                trControl = train_control)

browsing.res.C45Model <- train(isTarget ~., method="J48", data=browsing.res.dtrain,
                tuneLength = 5,
                trControl = train_control)
```


## Validation - browsing - C45 - Lab
```{r}
browsing.lab.C45Model$finalModel

print("lab")
predictions.lab.lab = predict(browsing.lab.C45Model, newdata = browsing.lab.dtest)
confMatrixes.lab.lab <- confusionMatrix(predictions.lab.lab, browsing.lab.dtest$isTarget)
eva.browsing.c45.lab.lab <- confMatrixes.lab.lab$byClass
eva.browsing.c45.lab.lab
confMatrixes.lab.lab$overall

print("res")
predictions.lab.res = predict(browsing.lab.C45Model, newdata = browsing.res.dtest)
confMatrixes.lab.res <- confusionMatrix(predictions.lab.res, browsing.res.dtest$isTarget)
eva.browsing.c45.lab.res <- confMatrixes.lab.res$byClass
eva.browsing.c45.lab.res
confMatrixes.lab.res$overall
```


## Validation - browsing - C45 - res
```{r}
browsing.res.C45Model$finalModel

print("lab")
predictions.res.lab = predict(browsing.res.C45Model, newdata = browsing.lab.dtest)
confMatrixes.res.lab <- confusionMatrix(predictions.res.lab, browsing.lab.dtest$isTarget)
eva.browsing.c45.res.lab <- confMatrixes.res.lab$byClass
eva.browsing.c45.res.lab
confMatrixes.res.lab$overall

print("res")
predictions.res.res = predict(browsing.res.C45Model, newdata = browsing.res.dtest)
confMatrixes.res.res <- confusionMatrix(predictions.res.res, browsing.res.dtest$isTarget)
eva.browsing.c45.res.res <- confMatrixes.res.res$byClass
eva.browsing.c45.res.res
confMatrixes.res.res$overall

```


## Models - Random Forest - browsing
```{r}

# Fitting Random Forest to the train dataset
set.seed(1003)  # Setting seed
repeat_cv <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

browsing.lab.classifier_RF = randomForest(x = browsing.lab.dtrain[-74],
                             y = browsing.lab.dtrain$isTarget,
                             ntree = 500,
                             trControl = repeat_cv)

browsing.res.classifier_RF = randomForest(x = browsing.res.dtrain[-74],
                             y = browsing.res.dtrain$isTarget,
                             ntree = 500,
                             trControl = repeat_cv)

# Importance plot
importance(browsing.lab.classifier_RF)
importance(browsing.res.classifier_RF)
  
# Variable importance plot
varImpPlot(browsing.lab.classifier_RF)
varImpPlot(browsing.res.classifier_RF)

```


## Validation - Random Forest - lab
```{r}

print("lab")
predictions.lab.lab.rf = predict(browsing.lab.classifier_RF, newdata = browsing.lab.dtest)
confMatrixes.lab.lab.rf <- confusionMatrix(predictions.lab.lab.rf, browsing.lab.dtest$isTarget)
eva.browsing.lab.lab.rf <- confMatrixes.lab.lab.rf$byClass
eva.browsing.lab.lab.rf
confMatrixes.lab.lab.rf$overall

print("res")
predictions.lab.res.rf = predict(browsing.lab.classifier_RF, newdata = browsing.res.dtest)
confMatrixes.lab.res.rf <- confusionMatrix(predictions.lab.res.rf, browsing.res.dtest$isTarget)
eva.browsing.lab.res.rf <- confMatrixes.lab.res.rf$byClass
eva.browsing.lab.res.rf
confMatrixes.lab.res.rf$overall

```


## Validation - Random Forest - res
```{r}

print("lab")
predictions.res.lab.rf = predict(browsing.res.classifier_RF, newdata = browsing.lab.dtest)
confMatrixes.res.lab.rf <- confusionMatrix(predictions.res.lab.rf, browsing.lab.dtest$isTarget)
eva.browsing.res.lab.rf <- confMatrixes.res.lab.rf$byClass
eva.browsing.res.lab.rf
confMatrixes.res.lab.rf$overall

print("res")
predictions.res.res.rf = predict(browsing.res.classifier_RF, newdata = browsing.res.dtest)
confMatrixes.res.res.rf <- confusionMatrix(predictions.res.res.rf, browsing.res.dtest$isTarget)
eva.browsing.res.res.rf <- confMatrixes.res.res.rf$byClass
eva.browsing.res.res.rf
confMatrixes.res.res.rf$overall


```

## Drop no-numeric columns
```{r}
library(glmnet)
library(tidyverse)
browsing.lab.dtrain <- browsing.lab.dtrain[, !(names(browsing.lab.dtrain) %in% c("X.dir", "ipOptCpCl_Num"))]
browsing.res.dtrain <- browsing.res.dtrain[, !(names(browsing.res.dtrain) %in% c("X.dir", "ipOptCpCl_Num"))]
browsing.lab.dtrain
browsing.res.dtrain

browsing.lab.dtest <- browsing.lab.dtest[, !(names(browsing.lab.dtest) %in% c("X.dir", "ipOptCpCl_Num"))]
browsing.res.dtest <- browsing.res.dtest[, !(names(browsing.res.dtest) %in% c("X.dir", "ipOptCpCl_Num"))]
browsing.lab.dtest
browsing.res.dtest

```


## Models - LASSO - Lab - browsing
```{r}
#perform k-fold cross-validation to find optimal lambda value
lambdas_to_try <- 10^seq(-3, 5, length.out = 100)
x.lab = as.matrix(browsing.lab.dtrain[-73])

cv_model.lab <- cv.glmnet(x.lab, browsing.lab.dtrain$isTarget, alpha = 1,
                      lambda = lambdas_to_try,
                      standardize = TRUE,
                      nfolds = 10,
                      family = "binomial")

#find optimal lambda value that minimizes test MSE
best_lambda.lab <- cv_model.lab$lambda.min
best_lambda.lab

#produce plot of test MSE by lambda value
plot(cv_model.lab) 

cv_best_model.lab <- glmnet(x.lab, browsing.lab.dtrain$isTarget, alpha = 1,
                      lambda = best_lambda.lab,
                      standardize = TRUE,
                      family = "binomial")

```

## Models - LASSO - Res - browsing
```{r}
#perform k-fold cross-validation to find optimal lambda value
lambdas_to_try <- 10^seq(-3, 5, length.out = 100)
x.res = as.matrix(browsing.res.dtrain[-73])

cv_model.res <- cv.glmnet(x.res, browsing.res.dtrain$isTarget, alpha = 1,
                      lambda = lambdas_to_try,
                      standardize = TRUE,
                      nfolds = 10,
                      family = "binomial")

#find optimal lambda value that minimizes test MSE
best_lambda.res <- cv_model.res$lambda.min
best_lambda.res

#produce plot of test MSE by lambda value
plot(cv_model.res) 

cv_best_model.res <- glmnet(x.res, browsing.res.dtrain$isTarget, alpha = 1,
                      lambda = best_lambda.lab,
                      standardize = TRUE,
                      family = "binomial")


```

## Validation - LASSO - Lab
```{r}
dtest.lab <- as.matrix(browsing.lab.dtest[-73])
ncol(dtest.lab)
dtest.res <- as.matrix(browsing.res.dtest[-73])
threshold <- 0.5


predictions.lab.lab.lasso <- predict(cv_best_model.lab, s = best_lambda.lab, dtest.lab, type = "response")
predictions.lab.res.lasso <- predict(cv_best_model.lab, s = best_lambda.res, dtest.res, type = "response")
predicted_classes.lab.lab <- ifelse(predictions.lab.lab.lasso > threshold,1,0)
predicted_classes.lab.res <- ifelse(predictions.lab.res.lasso > threshold,1,0)

confmtx.lab.lab.lasso <- confusionMatrix(table(predicted_classes.lab.lab,browsing.lab.dtest$isTarget))
confmtx.lab.res.lasso <- confusionMatrix(table(predicted_classes.lab.res,browsing.res.dtest$isTarget))

print("lab")
confmtx.lab.lab.lasso$byClass
confmtx.lab.lab.lasso$overall

print("res")
confmtx.lab.res.lasso$byClass
confmtx.lab.res.lasso$overall

```


## Validation - LASSO - Res
```{r}
predictions.res.lab.lasso <- predict(cv_best_model.res, s = best_lambda.lab, dtest.lab, type = "response")
predictions.res.res.lasso <- predict(cv_best_model.res, s = best_lambda.res, dtest.res, type = "response")
predicted_classes.res.lab <- ifelse(predictions.res.lab.lasso > threshold,1,0)
predicted_classes.res.res <- ifelse(predictions.res.res.lasso > threshold,1,0)

confmtx.res.lab.lasso <- confusionMatrix(table(predicted_classes.res.lab,browsing.lab.dtest$isTarget))
confmtx.res.res.lasso <- confusionMatrix(table(predicted_classes.res.res,browsing.res.dtest$isTarget))

print("lab")
confmtx.res.lab.lasso$byClass
confmtx.res.lab.lasso$overall

print("res")
confmtx.res.res.lasso$byClass
confmtx.res.res.lasso$overall

```