---
output:
  pdf_document: default
  html_document: default
---
### Preparation

Run this cell to clear the variables in your global R environment.

```{r}
rm(list = ls())
ls()
```

## Libraries

```{r}
library(caret)
library(RWeka)
library(dplyr)
```


## Data files
```{r}
slack.lab.1.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab1_flows.csv")
slack.lab.1.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab1_1111_flows.csv")
slack.lab.1.noVPN
slack.lab.1.1111

# Drop Src.ipaddr && Dest.ipaddr && start,end time && mac
drops <- c("srcIP",  "dstIP","srcMac", "dstMac", "timeFirst", "timeLast",
          "srcIPCC", "dstIPCC", "srcIPOrg", "dstIPOrg", "srcMac_dstMac_numP", "dstPortClass", "srcMacLbl_dstMacLbl", "ethVlanID",
          "hdrDesc",
          "vlanID",
          "icmpBFTypH_TypL_Code")

#"srcIPOrg", "dstIPOrg", 
slack.lab.1.noVPN <- slack.lab.1.noVPN[, !(names(slack.lab.1.noVPN) %in% drops)]
slack.lab.1.1111 <- slack.lab.1.1111[, !(names(slack.lab.1.1111) %in% drops)]
print("NA cols in slack.lab.1.noVPN:")
sum(is.na(slack.lab.1.noVPN))
print("NA cols in slack.lab.1.1111:")
sum(is.na(slack.lab.1.1111))

# Add a new column, isVPN, set to 0 for no_vpn, 1 for 1111
slack.lab.1.noVPN$isVPN <- 0
slack.lab.1.1111$isVPN <- 1

# Show summary

slack.lab.1.noVPN = data.frame(slack.lab.1.noVPN)
slack.lab.1.1111 = data.frame(slack.lab.1.1111)
```

## Prepare Data

```{r}
# Find length of the no_vpn table
slack.lab.1.nNoVPN = length(slack.lab.1.noVPN$flowInd)
slack.lab.1.nNoVPN

# Find length of the vpn table
slack.lab.1.nVPN = length(slack.lab.1.1111$flowInd)
slack.lab.1.nVPN

if (slack.lab.1.nNoVPN > slack.lab.1.nVPN) {
  slack.lab.1.nTrain = slack.lab.1.nVPN*0.7
} else {
  slack.lab.1.nTrain = slack.lab.1.nNoVPN*0.7
}

# Define Training set & Testing set
slack.lab.1.prop = slack.lab.1.nTrain/(nrow(slack.lab.1.noVPN))
set.seed(123)
slack.lab.1.noVPN.trnRows  <- sample(nrow(slack.lab.1.noVPN),nrow(slack.lab.1.noVPN)*slack.lab.1.prop)
slack.lab.1.noVPN.dtrain <- slack.lab.1.noVPN[ slack.lab.1.noVPN.trnRows,]
slack.lab.1.noVPN.dtest  <- slack.lab.1.noVPN[-slack.lab.1.noVPN.trnRows,]

slack.lab.1.1111.trnRows  <- sample(nrow(slack.lab.1.1111),nrow(slack.lab.1.1111)*0.7)
slack.lab.1.1111.dtrain <- slack.lab.1.1111[ slack.lab.1.1111.trnRows,]
slack.lab.1.1111.dtest  <- slack.lab.1.1111[-slack.lab.1.1111.trnRows,]

slack.lab.1.dtrain <- rbind(slack.lab.1.noVPN.dtrain,slack.lab.1.1111.dtrain)
slack.lab.1.dtest <- rbind(slack.lab.1.1111.dtest,slack.lab.1.noVPN.dtest)

# Remove all columns with only 1 unique value
s <- slack.lab.1.dtrain %>% select(where(~ n_distinct(.) <= 1))
drops <- c(drops,colnames(s))
length(drops)
slack.lab.1.dtrain <- slack.lab.1.dtrain %>% select(where(~ n_distinct(.) > 1))
slack.lab.1.dtrain$isVPN <- as.factor(slack.lab.1.dtrain$isVPN)

slack.lab.1.dtest <- slack.lab.1.dtest %>% select(where(~ n_distinct(.) > 1))
slack.lab.1.dtest$isVPN <- as.factor(slack.lab.1.dtest$isVPN)

nrow(slack.lab.1.dtest)
nrow(slack.lab.1.dtrain)
ncol(slack.lab.1.dtrain)
```


## Train Model

```{r}

train_control<- trainControl(method="cv", number=10)
slack.lab.1.C45Model <- train(isVPN ~., method="J48", data=slack.lab.1.dtrain,
                tuneLength = 5,
                trControl = train_control)

```



## Validation
```{r}
slack.lab.1.C45Model
slack.lab.1.C45Model$finalModel


predictions = predict(slack.lab.1.C45Model, newdata = slack.lab.1.dtest)
confusionMatrix(predictions, slack.lab.1.dtest$isVPN)
```


## Load more files
```{r}
# Remain data in lab
slack.lab.10.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab10re_flows.csv")
slack.lab.10.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab10_1111_flows.csv")
slack.lab.3.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab3_flows.csv")
slack.lab.3.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab3_1111_flows.csv")
slack.lab.6.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab6_flows.csv")
slack.lab.6.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab6_1111_flows.csv")
slack.lab.8.noVPN = read.csv("t2/slack/none/lab/slackPcapFixGapLab8_flows.csv")
slack.lab.8.1111 = read.csv("t2/slack/1.1.1.1/lab/slackPcapFixGapLab8_1111_flows.csv")


# Data in residence
slack.res.10.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes11_flows.csv")
slack.res.10.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes10_1111_flows.csv")
slack.res.1.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes1_flows.csv")
slack.res.1.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes1_1111_flows.csv")
slack.res.3.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes3_flows.csv")
slack.res.3.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes3_1111_flows.csv")
slack.res.6.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes6_flows.csv")
slack.res.6.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes6_1111_flows.csv")
slack.res.8.noVPN = read.csv("t2/slack/none/res/slackPcapFixGapRes8_flows.csv")
slack.res.8.1111 = read.csv("t2/slack/1.1.1.1/res/slackPcapFixGapRes8_1111_flows.csv")

```

## Data file process function
```{r}
load_data <- function(data) {
  data.noVPN <- get(paste(data, "noVPN", sep = "."))
  data.1111 <- get(paste(data, "1111", sep = "."))
  
  data.noVPN <- data.noVPN[, !(names(data.noVPN) %in% drops)]
  data.1111 <- data.1111[, !(names(data.1111) %in% drops)]
  
  data.noVPN$isVPN <- 0
  data.1111$isVPN <- 1
  
  data.noVPN = data.frame(data.noVPN)
  data.1111 = data.frame(data.1111)
  data.data <- rbind(data.1111,data.noVPN)
  
  assign(paste(data, "noVPN", sep = "."), data.noVPN, envir = globalenv())
  assign(paste(data, "1111", sep = "."), data.1111, envir = globalenv())
  assign(paste(data, "data", sep = "."), data.data, envir = globalenv())
}
```

```{r}
load_data("slack.res.10")
load_data("slack.res.1")
load_data("slack.res.3")
load_data("slack.res.6")
load_data("slack.res.8")

load_data("slack.lab.10")
load_data("slack.lab.1")
load_data("slack.lab.3")
load_data("slack.lab.6")
load_data("slack.lab.8")
```

## Predicate
```{r}
predictions.lab.10 = predict(slack.lab.1.C45Model, newdata = slack.lab.10.data)
confMatrixes.lab.10 <- confusionMatrix(predictions.lab.10, as.factor(slack.lab.10.data$isVPN))

predictions.lab.3 = predict(slack.lab.1.C45Model, newdata = slack.lab.3.data)
confMatrixes.lab.3 <- confusionMatrix(predictions.lab.3, as.factor(slack.lab.3.data$isVPN))

predictions.lab.6 = predict(slack.lab.1.C45Model, newdata = slack.lab.6.data)
confMatrixes.lab.6 <- confusionMatrix(predictions.lab.6, as.factor(slack.lab.6.data$isVPN))

predictions.lab.8 = predict(slack.lab.1.C45Model, newdata = slack.lab.8.data)
confMatrixes.lab.8 <- confusionMatrix(predictions.lab.8, as.factor(slack.lab.8.data$isVPN))

predictions.res.3 = predict(slack.lab.1.C45Model, newdata = slack.res.3.data)
confMatrixes.res.3 <- confusionMatrix(predictions.res.3, as.factor(slack.res.3.data$isVPN))

confMatrixes.lab.10$overall
confMatrixes.lab.3$overall
confMatrixes.lab.6$overall
confMatrixes.lab.8$overall
confMatrixes.res.3$overall
```


## Data process function
```{r}
process_slack_data <- function(data) {
  data.noVPN <- get(paste(data, "noVPN", sep = "."))
  data.1111 <- get(paste(data, "1111", sep = "."))
  
  data.prop = nrow(data.1111)*0.7 / nrow(data.noVPN)
  
  data.noVPN.trnRows  <- sample(nrow(data.noVPN),nrow(data.noVPN)*data.prop)
  data.noVPN.dtrain <- data.noVPN[ data.noVPN.trnRows,]
  data.noVPN.dtest  <- data.noVPN[-data.noVPN.trnRows,]

  data.1111.trnRows <- sample(nrow(data.1111),nrow(data.1111)*0.7)
  data.1111.dtrain <- data.1111[ data.1111.trnRows,]
  data.1111.dtest  <- data.1111[-data.1111.trnRows,]

  data.dtrain <- rbind(data.noVPN.dtrain,data.1111.dtrain)
  data.dtest <- rbind(data.noVPN.dtest,data.1111.dtest)

  data.dtrain$isVPN <- as.factor(data.dtrain$isVPN)
  data.dtest$isVPN <- as.factor(data.dtest$isVPN)
  
  assign(paste(data, "dtest", sep = "."), data.dtest, envir = globalenv())
  assign(paste(data, "dtrain", sep = "."), data.dtrain, envir = globalenv())
  assign(paste(data, "data", sep = "."), rbind(data.dtrain,data.dtest), envir = globalenv())
}

```


# Train model with more data
```{r}
slack.lab.noVPN <- rbind(slack.lab.10.noVPN,slack.lab.1.noVPN,slack.lab.3.noVPN,
                        slack.lab.6.noVPN,slack.lab.8.noVPN)
slack.lab.1111 <- rbind(slack.lab.10.1111,slack.lab.1.1111,slack.lab.3.1111,
                        slack.lab.6.1111,slack.lab.8.1111)

slack.res.noVPN <- rbind(slack.res.10.noVPN,slack.res.1.noVPN,slack.res.3.noVPN,
                         slack.res.6.noVPN,slack.res.8.noVPN)
slack.res.1111 <- rbind(slack.res.10.1111,slack.res.1.1111,slack.res.3.1111,
                        slack.res.6.1111,slack.res.8.1111)
slack.res.data <- rbind(slack.res.noVPN, slack.res.1111)
slack.res.data$isVPN <- as.factor(slack.res.data$isVPN)

nrow(slack.lab.noVPN)
nrow(slack.lab.1111)

process_slack_data("slack.lab")
slack.lab.dtrain

process_slack_data("slack.res")
slack.res.dtrain

slack.res.dtrain <- slack.res.dtrain %>% select(where(~ n_distinct(.) > 1))
slack.res.dtest <- slack.res.dtest %>% select(where(~ n_distinct(.) > 1))

slack.noVPN <- rbind(slack.lab.noVPN, slack.res.noVPN)
slack.1111 <- rbind(slack.lab.1111, slack.res.1111)
process_slack_data("slack")

```


```{r}
train_control<- trainControl(method="cv", number=10)
slack.lab.C45Model <- train(isVPN ~., method="J48", data=slack.lab.dtrain,
                tuneLength = 5,
                trControl = train_control)

slack.res.C45Model <- train(isVPN ~., method="J48", data=slack.res.dtrain,
                tuneLength = 5,
                trControl = train_control)

slack.C45Model <- train(isVPN ~., method="J48", data=slack.dtrain,
                tuneLength = 5,
                trControl = train_control)

```

```{r}
slack.lab.C45Model
slack.lab.C45Model$finalModel

predictions.lab.lab = predict(slack.lab.C45Model, newdata = slack.lab.dtest)
confMatrixes.lab.lab <- confusionMatrix(predictions.lab.lab, slack.lab.dtest$isVPN)

predictions.lab.res = predict(slack.lab.C45Model, newdata = slack.res.data)
confMatrixes.lab.res <- confusionMatrix(predictions.lab.res, slack.res.data$isVPN)

confMatrixes.lab.lab$overall
confMatrixes.lab.res$overall
```

```{r}
slack.res.C45Model
slack.res.C45Model$finalModel

predictions.res.lab = predict(slack.res.C45Model, newdata = slack.lab.dtest)
confMatrixes.res.lab <- confusionMatrix(predictions.res.lab, slack.lab.dtest$isVPN)

predictions.res.res = predict(slack.res.C45Model, newdata = slack.res.dtest)
confMatrixes.res.res <- confusionMatrix(predictions.res.res, slack.res.dtest$isVPN)

confMatrixes.res.lab$overall
confMatrixes.res.res$overall

```

```{r}
slack.C45Model
slack.C45Model$finalModel

predictions.lab = predict(slack.C45Model, newdata = slack.dtest)
confMatrixes.lab <- confusionMatrix(predictions.lab, slack.dtest$isVPN)

confMatrixes.lab$overall
```

# Try Random Forest Approach, Load packages
```{r}
# Loading package
library(caTools)
library(randomForest)
```

# Split Data
```{r}
# Splitting data in train and test data
split.lab <- sample.split(slack.lab.data, SplitRatio = 0.7)
split.lab

split.res <-  sample.split(slack.res.data, SplitRatio = 0.7)
split.res

slack.lab.rf.train <- subset(slack.lab.data, split.lab == "TRUE")
slack.lab.rf.test <- subset(slack.lab.data, split.lab == "FALSE")

slack.res.rf.train <-  subset(slack.res.data, split.res == "TRUE")
slack.res.rf.test <- subset(slack.res.data, split.res == "FALSE")

# Fitting Random Forest to the train dataset
set.seed(1003)  # Setting seed
repeat_cv <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

slack.lab.classifier_RF = randomForest(x = slack.lab.rf.train[-81],
                             y = slack.lab.rf.train$isVPN,
                             ntree = 500,
                             trControl = repeat_cv)

slack.res.classifier_RF = randomForest(x = slack.res.rf.train[-81],
                             y = slack.res.rf.train$isVPN,
                             ntree = 500,
                             trControl = repeat_cv)

# Importance plot
importance(slack.lab.classifier_RF)
importance(slack.res.classifier_RF)
  
# Variable importance plot
varImpPlot(slack.lab.classifier_RF)
varImpPlot(slack.res.classifier_RF)
```


# Validation & Prediction
```{r}
# Predicting the Test set results
y_pred.lab = predict(slack.lab.classifier_RF, newdata = slack.lab.rf.test[-81])
y_pred.lab.res = predict(slack.lab.classifier_RF, newdata = slack.res.data[-81])

# Confusion Matrix
confusion_mtx.lab = confusionMatrix(y_pred.lab, slack.lab.rf.test$isVPN)
confusion_mtx.lab.res = confusionMatrix(y_pred.lab.res, slack.res.data$isVPN)
confusion_mtx.lab
confusion_mtx.lab.res$overall


# Predicting the Test set results
y_pred.res = predict(slack.res.classifier_RF, newdata = slack.res.rf.test[-81])
y_pred.res.lab = predict(slack.res.classifier_RF, newdata = slack.lab.data[-81])

# Confusion Matrix
confusion_mtx.res = confusionMatrix(y_pred.res, slack.res.rf.test$isVPN)
confusion_mtx.res.lab = confusionMatrix(y_pred.res.lab, slack.lab.data$isVPN)
confusion_mtx.res
confusion_mtx.res.lab$overall
```

## Tuned RF
```{r}

slack.lab.tuned_RF = tuneRF(x = slack.lab.rf.train[-81],
                            y = slack.lab.rf.train$isVPN,
                            mtryStart = 1,
                            ntreeTry = 500,
                            stepFactor=2, improve=0.05,
                            trace=TRUE, doBest = TRUE 
                             )

#slack.res.classifier_RF = tuneRF(x = slack.res.rf.train[-81],
                             #y = slack.res.rf.train$isVPN,
                             #ntree = 500,
                             #trControl = repeat_cv)


tune.pred.lab.res = predict(slack.lab.tuned_RF, newdata = slack.res.data[-81])
confusion_mtx.tune.lab.res = confusionMatrix(tune.pred.lab.res, slack.res.data$isVPN)
confusion_mtx.tune.lab.res$overall

tune.pred.lab.lab = predict(slack.lab.tuned_RF, newdata = slack.lab.data[-81])
confusion_mtx.tune.lab.lab = confusionMatrix(tune.pred.lab.lab, slack.lab.data$isVPN)
confusion_mtx.tune.lab.lab$overall
```



# Load noARP Files
```{r}
# Data in residence
slack.res.10.noVPN.noARP = read.csv("t2/slack/none/res/noARP/slackPcapFixGapRes11_noARP_flows.csv")
slack.res.10.1111.noARP = read.csv("t2/slack/1.1.1.1/res/noARP/slackPcapFixGapRes10_1111_noARP_flows.csv")
slack.res.1.noVPN.noARP = read.csv("t2/slack/none/res/noARP/slackPcapFixGapRes1_noARP_flows.csv")
slack.res.1.1111.noARP = read.csv("t2/slack/1.1.1.1/res/noARP/slackPcapFixGapRes1_1111_noARP_flows.csv")
slack.res.3.noVPN.noARP = read.csv("t2/slack/none/res/noARP/slackPcapFixGapRes3_noARP_flows.csv")
slack.res.3.1111.noARP = read.csv("t2/slack/1.1.1.1/res/noARP/slackPcapFixGapRes3_1111_noARP_flows.csv")
slack.res.6.noVPN.noARP = read.csv("t2/slack/none/res/noARP/slackPcapFixGapRes6_noARP_flows.csv")
slack.res.6.1111.noARP = read.csv("t2/slack/1.1.1.1/res/noARP/slackPcapFixGapRes6_1111_noARP_flows.csv")
slack.res.8.noVPN.noARP = read.csv("t2/slack/none/res/noARP/slackPcapFixGapRes8_noARP_flows.csv")
slack.res.8.1111.noARP = read.csv("t2/slack/1.1.1.1/res/noARP/slackPcapFixGapRes8_1111_noARP_flows.csv")

# Data in residence
slack.res.10.noVPN.noARP <- slack.res.10.noVPN.noARP[, !(names(slack.res.10.noVPN.noARP) %in% drops)]
slack.res.10.1111.noARP <- slack.res.10.1111.noARP[, !(names(slack.res.10.1111.noARP) %in% drops)]
slack.res.1.noVPN.noARP <- slack.res.1.noVPN.noARP[, !(names(slack.res.1.noVPN.noARP) %in% drops)]
slack.res.1.1111.noARP <- slack.res.1.1111.noARP[, !(names(slack.res.1.1111.noARP) %in% drops)]
slack.res.3.noVPN.noARP <- slack.res.3.noVPN.noARP[, !(names(slack.res.3.noVPN.noARP) %in% drops)]
slack.res.3.1111.noARP <- slack.res.3.1111.noARP[, !(names(slack.res.3.1111.noARP) %in% drops)]
slack.res.6.noVPN.noARP <- slack.res.6.noVPN.noARP[, !(names(slack.res.6.noVPN.noARP) %in% drops)]
slack.res.6.1111.noARP <- slack.res.6.1111.noARP[, !(names(slack.res.6.1111.noARP) %in% drops)]
slack.res.8.noVPN.noARP <- slack.res.8.noVPN.noARP[, !(names(slack.res.8.noVPN.noARP) %in% drops)]
slack.res.8.1111.noARP <- slack.res.8.1111.noARP[, !(names(slack.res.8.1111.noARP) %in% drops)]

# Data in residence
slack.res.10.noVPN.noARP$isVPN <- 0
slack.res.10.1111.noARP$isVPN <- 1
slack.res.1.noVPN.noARP$isVPN <- 0
slack.res.1.1111.noARP$isVPN <- 1
slack.res.3.noVPN.noARP$isVPN <- 0
slack.res.3.1111.noARP$isVPN <- 1
slack.res.6.noVPN.noARP$isVPN <- 0
slack.res.6.1111.noARP$isVPN <- 1
slack.res.8.noVPN.noARP$isVPN <- 0
slack.res.8.1111.noARP$isVPN <- 1

slack.res.10.noVPN.noARP = data.frame(slack.res.10.noVPN.noARP)
slack.res.10.1111.noARP = data.frame(slack.res.10.1111.noARP)
slack.res.1.noVPN.noARP = data.frame(slack.res.1.noVPN.noARP)
slack.res.1.1111.noARP = data.frame(slack.res.1.1111.noARP)
slack.res.3.noVPN.noARP = data.frame(slack.res.3.noVPN.noARP)
slack.res.3.1111.noARP = data.frame(slack.res.3.1111.noARP)
slack.res.6.noVPN.noARP = data.frame(slack.res.6.noVPN.noARP)
slack.res.6.1111.noARP = data.frame(slack.res.6.1111.noARP)
slack.res.8.noVPN.noARP = data.frame(slack.res.8.noVPN.noARP)
slack.res.8.1111.noARP = data.frame(slack.res.8.1111.noARP)

slack.res.noVPN.noARP <- rbind(slack.res.10.noVPN.noARP,slack.res.1.noVPN.noARP,slack.res.3.noVPN.noARP,
                         slack.res.6.noVPN.noARP,slack.res.8.noVPN.noARP)
slack.res.1111.noARP <- rbind(slack.res.10.1111.noARP,slack.res.1.1111.noARP,slack.res.3.1111.noARP,
                        slack.res.6.1111.noARP,slack.res.8.1111.noARP)
slack.res.data.noARP <- rbind(slack.res.noVPN.noARP, slack.res.1111.noARP)
slack.res.data.noARP$isVPN <- as.factor(slack.res.data.noARP$isVPN)

```

# Predict again
```{r}
# C4.5
predictions.lab.res.noARP = predict(slack.lab.C45Model, newdata = slack.res.data.noARP)
confMatrixes.lab.res.noARP <- confusionMatrix(predictions.lab.res.noARP, slack.res.data.noARP$isVPN)

confMatrixes.lab.res.noARP$overall

# Random Forest
y_pred.lab.res.noARP = predict(slack.lab.classifier_RF, newdata = slack.res.data.noARP[-81])
confusion_mtx.lab.res.noARP = confusionMatrix(y_pred.lab.res.noARP, slack.res.data.noARP$isVPN)
confusion_mtx.lab.res.noARP$overall

tune.pred.lab.res.noARP = predict(slack.lab.tuned_RF, newdata = slack.res.data.noARP[-81])
confusion_mtx.tune.lab.res.noARP = confusionMatrix(tune.pred.lab.res.noARP, slack.res.data.noARP$isVPN)
confusion_mtx.tune.lab.res.noARP$overall
```

## For Streaming, Load files
```{r}
twitch.lab.10.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab10_flows.csv")
twitch.lab.1.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab1_flows.csv")
twitch.lab.3.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab3_flows.csv")
twitch.lab.6.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab6_flows.csv")
twitch.lab.8.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab8_flows.csv")

twitch.lab.10.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab10_1111_flows.csv")
twitch.lab.1.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab1_1111_flows.csv")
twitch.lab.3.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab3_1111_flows.csv")
twitch.lab.6.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab6_1111_flows.csv")
twitch.lab.8.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab8_1111_flows.csv")

twitch.res.10.noVPN = read.csv("t2/streaming/none/res/streamingCapRes10_flows.csv")
twitch.res.1.noVPN = read.csv("t2/streaming/none/res/streamingCapRes1_flows.csv")
twitch.res.3.noVPN = read.csv("t2/streaming/none/res/streamingCapRes3_flows.csv")
twitch.res.6.noVPN = read.csv("t2/streaming/none/res/streamingCapRes6_flows.csv")
twitch.res.8.noVPN = read.csv("t2/streaming/none/res/streamingCapRes8_flows.csv")

load_data("twitch.lab.10")
load_data("twitch.lab.1")
load_data("twitch.lab.3")
load_data("twitch.lab.6")
load_data("twitch.lab.8")

twitch.lab.noVPN <- rbind(twitch.lab.10.noVPN,twitch.lab.1.noVPN,twitch.lab.3.noVPN,
                        twitch.lab.6.noVPN,twitch.lab.8.noVPN)
twitch.lab.1111 <- rbind(twitch.lab.10.1111,twitch.lab.1.1111,twitch.lab.3.1111,
                        twitch.lab.6.1111,twitch.lab.8.1111)
twitch.lab.data <- rbind(twitch.lab.noVPN,twitch.lab.1111)

twitch.lab.1111

twitch.lab.data


```
```{r}
predictions.slack.twitch.lab.c45 = predict(slack.res.C45Model, newdata = twitch.lab.data)
confMatrixes.slack.twitch.lab.c45 <- confusionMatrix(table(predictions.slack.twitch.lab.c45, twitch.lab.data$isVPN))
confMatrixes.slack.twitch.lab.c45$overall
```


# Try apply some regulation - Lasso, Load library     
```{r}
library(glmnet)
library(tidyverse)
```


```{r}

#perform k-fold cross-validation to find optimal lambda value
#slack.lab.data <- slack.lab.data[, !(names(slack.lab.1.1111) %in% c("X.dir", "ipOptCpCl_Num"))]
lambdas_to_try <- 10^seq(-3, 5, length.out = 100)
slack.lab.data
x = as.matrix(slack.lab.data[-79])

cv_model <- cv.glmnet(x, slack.lab.data$isVPN, alpha = 1,
                      lambda = lambdas_to_try,
                      standardize = TRUE,
                      nfolds = 10,
                      family = "binomial")

#find optimal lambda value that minimizes test MSE
best_lambda <- cv_model$lambda.min
best_lambda

#produce plot of test MSE by lambda value
plot(cv_model) 

cv_best_model <- glmnet(x, slack.lab.data$isVPN, alpha = 1,
                      lambda = lambdas_to_try,
                      standardize = TRUE,
                      family = "binomial")



```