---
output:
  pdf_document: default
  html_document: default
---

### Preparation

Run this cell to clear the variables in your global R environment.

```{r}
rm(list = ls())
ls()
```

## Libraries

```{r}
library(caret)
library(RWeka)
library(dplyr)
library(caTools)
library(randomForest)
```


## Define basics
```{r}
# Drop Src.ipaddr && Dest.ipaddr && start,end time && mac
drops <- c("srcIP",  "dstIP","srcMac", "dstMac", "timeFirst", "timeLast",
          "srcIPCC", "dstIPCC", "srcIPOrg", "dstIPOrg", "srcMac_dstMac_numP", "dstPortClass", "srcMacLbl_dstMacLbl", "ethVlanID",
          "hdrDesc",
          "vlanID",
          "icmpBFTypH_TypL_Code", "ipOptCnt", "ipOptCpCl_Num")

```


## Data file process function
```{r}
load_data <- function(data) {
  data.noVPN <- get(paste(data, "noVPN", sep = "."))
  data.1111 <- get(paste(data, "1111", sep = "."))
  
  data.noVPN <- data.noVPN[, !(names(data.noVPN) %in% drops)]
  data.1111 <- data.1111[, !(names(data.1111) %in% drops)]
  
  data.noVPN$isVPN <- 0
  data.1111$isVPN <- 1
  
  data.noVPN = data.frame(data.noVPN)
  data.1111 = data.frame(data.1111)
  data.data <- rbind(data.1111,data.noVPN)
  
  assign(paste(data, "noVPN", sep = "."), data.noVPN, envir = globalenv())
  assign(paste(data, "1111", sep = "."), data.1111, envir = globalenv())
  assign(paste(data, "data", sep = "."), data.data, envir = globalenv())
}
```


## Load data files
```{r}
twitch.lab.10.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab10_flows.csv")
twitch.lab.1.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab1_flows.csv")
twitch.lab.3.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab3_flows.csv")
twitch.lab.6.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab6_flows.csv")
twitch.lab.8.noVPN = read.csv("t2/streaming/none/lab/streamingCapLab8_flows.csv")

twitch.lab.10.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab10_1111_flows.csv")
twitch.lab.1.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab1_1111_flows.csv")
twitch.lab.3.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab3_1111_flows.csv")
twitch.lab.6.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab6_1111_flows.csv")
twitch.lab.8.1111 = read.csv("t2/streaming/1.1.1.1/lab/streamingCapLab8_1111_flows.csv")

twitch.res.10.noVPN = read.csv("t2/streaming/none/res/streamingCapRes10_flows.csv")
twitch.res.1.noVPN = read.csv("t2/streaming/none/res/streamingCapRes1_flows.csv")
twitch.res.3.noVPN = read.csv("t2/streaming/none/res/streamingCapRes3_flows.csv")
twitch.res.6.noVPN = read.csv("t2/streaming/none/res/streamingCapRes6_flows.csv")
twitch.res.8.noVPN = read.csv("t2/streaming/none/res/streamingCapRes8_flows.csv")

twitch.res.10.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes10_1111_flows.csv")
twitch.res.1.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes1_1111_flows.csv")
twitch.res.3.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes3_1111_flows.csv")
twitch.res.6.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes6_1111_flows.csv")
twitch.res.8.1111 = read.csv("t2/streaming/1.1.1.1/res/streamingCapRes8_1111_flows.csv")

twitch.lab.noVPN <- rbind(twitch.lab.10.noVPN,twitch.lab.1.noVPN,twitch.lab.3.noVPN,
                        twitch.lab.6.noVPN,twitch.lab.8.noVPN)
twitch.lab.1111 <- rbind(twitch.lab.10.1111,twitch.lab.1.1111,twitch.lab.3.1111,
                        twitch.lab.6.1111,twitch.lab.8.1111)
twitch.lab.data <- rbind(twitch.lab.noVPN,twitch.lab.1111)

twitch.res.noVPN <- rbind(twitch.res.10.noVPN,twitch.res.1.noVPN,twitch.res.3.noVPN,
                          twitch.res.6.noVPN,twitch.res.8.noVPN)
twitch.res.1111 <- rbind(twitch.res.10.1111,twitch.res.1.1111,twitch.res.3.1111,
                         twitch.res.6.1111,twitch.res.8.1111)

twitch.data.noVPN <- rbind(twitch.lab.noVPN,twitch.res.noVPN)
twitch.data.1111 <- rbind(twitch.lab.1111,twitch.res.1111)
twitch.data <- rbind(twitch.data.1111,twitch.data.noVPN)


```


## Clean data - define cols to drop
```{r}
s <- twitch.data %>% select(where(~ n_distinct(.) <= 1))
drops <- c(drops,colnames(s))
drops

load_data("twitch.lab.10")
load_data("twitch.lab.1")
load_data("twitch.lab.3")
load_data("twitch.lab.6")
load_data("twitch.lab.8")

load_data("twitch.res.10")
load_data("twitch.res.1")
load_data("twitch.res.3")
load_data("twitch.res.6")
load_data("twitch.res.8")

twitch.lab.noVPN <- rbind(twitch.lab.10.noVPN,twitch.lab.1.noVPN,twitch.lab.3.noVPN,
                        twitch.lab.6.noVPN,twitch.lab.8.noVPN)
twitch.lab.1111 <- rbind(twitch.lab.10.1111,twitch.lab.1.1111,twitch.lab.3.1111,
                        twitch.lab.6.1111,twitch.lab.8.1111)
twitch.lab.data <- rbind(twitch.lab.noVPN,twitch.lab.1111)

twitch.res.noVPN <- rbind(twitch.res.10.noVPN,twitch.res.1.noVPN,twitch.res.3.noVPN,
                          twitch.res.6.noVPN,twitch.res.8.noVPN)
twitch.res.1111 <- rbind(twitch.res.10.1111,twitch.res.1.1111,twitch.res.3.1111,
                         twitch.res.6.1111,twitch.res.8.1111)

twitch.data.noVPN <- rbind(twitch.lab.noVPN,twitch.res.noVPN)
twitch.data.1111 <- rbind(twitch.lab.1111,twitch.res.1111)
twitch.data <- rbind(twitch.data.1111,twitch.data.noVPN)

```
## Process data function
```{r}
process_data <- function(data) {
  data.noVPN <- get(paste(data, "noVPN", sep = "."))
  data.1111 <- get(paste(data, "1111", sep = "."))
  
  data.prop = nrow(data.1111)*0.7 / nrow(data.noVPN)
  
  data.noVPN.trnRows  <- sample(nrow(data.noVPN),nrow(data.noVPN)*data.prop)
  data.noVPN.dtrain <- data.noVPN[ data.noVPN.trnRows,]
  data.noVPN.dtest  <- data.noVPN[-data.noVPN.trnRows,]

  data.1111.trnRows <- sample(nrow(data.1111),nrow(data.1111)*0.7)
  data.1111.dtrain <- data.1111[ data.1111.trnRows,]
  data.1111.dtest  <- data.1111[-data.1111.trnRows,]

  data.dtrain <- rbind(data.noVPN.dtrain,data.1111.dtrain)
  data.dtest <- rbind(data.noVPN.dtest,data.1111.dtest)

  data.dtrain$isVPN <- as.factor(data.dtrain$isVPN)
  data.dtest$isVPN <- as.factor(data.dtest$isVPN)
  
  assign(paste(data, "dtest", sep = "."), data.dtest, envir = globalenv())
  assign(paste(data, "dtrain", sep = "."), data.dtrain, envir = globalenv())
  assign(paste(data, "data", sep = "."), rbind(data.dtrain,data.dtest), envir = globalenv())
}

```


## Process data for trainning
```{r}
process_data("twitch.lab")
process_data("twitch.res")

```

## Models - C45
```{r}
train_control<- trainControl(method="cv", number=10)
twitch.lab.C45Model <- train(isVPN ~., method="J48", data=twitch.lab.dtrain,
                tuneLength = 5,
                trControl = train_control)

twitch.res.C45Model <- train(isVPN ~., method="J48", data=twitch.res.dtrain,
                tuneLength = 5,
                trControl = train_control)

```


## Validation - C45 - lab
```{r}
twitch.lab.C45Model$finalModel

print("lab")
predictions.lab.lab = predict(twitch.lab.C45Model, newdata = twitch.lab.dtest)
confMatrixes.lab.lab <- confusionMatrix(predictions.lab.lab, twitch.lab.dtest$isVPN)
eva.twitch.c45.lab.lab <- confMatrixes.lab.lab$byClass
eva.twitch.c45.lab.lab
confMatrixes.lab.lab$overall

print("res")
predictions.lab.res = predict(twitch.lab.C45Model, newdata = twitch.res.data)
confMatrixes.lab.res <- confusionMatrix(predictions.lab.res, twitch.res.data$isVPN)
eva.twitch.c45.lab.res <- confMatrixes.lab.res$byClass
eva.twitch.c45.lab.res
confMatrixes.lab.res$overall
```


## Validation - C45 - res
```{r}
twitch.res.C45Model$finalModel

print("res")
predictions.res.res = predict(twitch.res.C45Model, newdata = twitch.res.dtest)
confMatrixes.res.res <- confusionMatrix(predictions.res.res, twitch.res.dtest$isVPN)
eva.twitch.c45.res.res <- confMatrixes.res.res$byClass
eva.twitch.c45.res.res
confMatrixes.res.res$overall

print("lab")
predictions.res.lab = predict(twitch.res.C45Model, newdata = twitch.lab.data)
confMatrixes.res.lab <- confusionMatrix(predictions.res.lab, twitch.lab.data$isVPN)
eva.twitch.c45.res.lab <- confMatrixes.res.lab$byClass
eva.twitch.c45.res.lab
confMatrixes.res.lab$overall

```

## Models - Random Forest
```{r}

# Fitting Random Forest to the train dataset
set.seed(1003)  # Setting seed
repeat_cv <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

twitch.lab.classifier_RF = randomForest(x = twitch.lab.dtrain[-81],
                             y = twitch.lab.dtrain$isVPN,
                             ntree = 500,
                             trControl = repeat_cv)

twitch.res.classifier_RF = randomForest(x = twitch.res.dtrain[-81],
                             y = twitch.res.dtrain$isVPN,
                             ntree = 500,
                             trControl = repeat_cv)

# Importance plot
importance(twitch.lab.classifier_RF)
importance(twitch.res.classifier_RF)
  
# Variable importance plot
varImpPlot(twitch.lab.classifier_RF)
varImpPlot(twitch.res.classifier_RF)

```


## Validation - Random Forest - lab
```{r}

print("lab")
predictions.lab.lab.rf = predict(twitch.lab.classifier_RF, newdata = twitch.lab.dtest)
confMatrixes.lab.lab.rf <- confusionMatrix(predictions.lab.lab.rf, twitch.lab.dtest$isVPN)
eva.twitch.c45.lab.lab.rf <- confMatrixes.lab.lab.rf$byClass
eva.twitch.c45.lab.lab.rf
confMatrixes.lab.lab.rf$overall

print("res")
predictions.lab.res.rf = predict(twitch.lab.classifier_RF, newdata = twitch.res.data)
confMatrixes.lab.res.rf <- confusionMatrix(predictions.lab.res.rf, twitch.res.data$isVPN)
eva.twitch.c45.lab.res.rf <- confMatrixes.lab.res.rf$byClass
eva.twitch.c45.lab.res.rf
confMatrixes.lab.res.rf$overall

```


## Validation - Random Forest - res
```{r}
print("res")
predictions.res.res.rf = predict(twitch.res.classifier_RF, newdata = twitch.res.dtest)
confMatrixes.res.res.rf <- confusionMatrix(predictions.res.res.rf, twitch.res.dtest$isVPN)
eva.twitch.c45.res.res.rf <- confMatrixes.res.res.rf$byClass
eva.twitch.c45.res.res.rf
confMatrixes.res.res.rf$overall

print("lab")
predictions.res.lab.rf = predict(twitch.res.classifier_RF, newdata = twitch.lab.data)
confMatrixes.res.lab.rf <- confusionMatrix(predictions.res.lab.rf, twitch.lab.data$isVPN)
eva.twitch.c45.res.lab.rf <- confMatrixes.res.lab.rf$byClass
eva.twitch.c45.res.lab.rf
confMatrixes.res.lab.rf$overall
```

## Packages - lightGBM
```{r}
library(lightgbm)
library(caret)
library(ggplot2) 
twitch.lab.dtrain

```


## Models - lightGBM - Lab
```{r}
set.seed(1003)
twitch.lab.dtrain <- twitch.lab.dtrain[, !(names(twitch.lab.dtrain) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.res.dtrain <- twitch.res.dtrain[, !(names(twitch.res.dtrain) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.lab.dtest <- twitch.lab.dtest[, !(names(twitch.lab.dtest) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.res.dtest <- twitch.res.dtest[, !(names(twitch.res.dtest) %in% c("X.dir", "ipOptCpCl_Num"))]

# Define parameters
params <- list(
  objective = "binary"
  , num_leaves = 4L
  , learning_rate = 1.0
)

x_train.lab <- as.matrix(twitch.lab.dtrain[-80])
x_test.lab <- as.matrix(twitch.lab.dtest[-80])

twitch.lab.dtrain.gbm <- lgb.Dataset(x_train.lab, label = twitch.lab.dtrain$isVPN, free_raw_data = FALSE)
twitch.lab.dtest.gbm <- lgb.Dataset(x_test.lab, label = twitch.lab.dtest$isVPN, free_raw_data = FALSE)

# Validation data
valids <- list(train = twitch.lab.dtrain.gbm, test = twitch.lab.dtest.gbm)

model <- lgb.train(
  params
  , data = twitch.lab.dtrain.gbm
  , nrounds = 10L
  , verbose = -1L
)

```

```{r}
# prediction
predictions <- predict(model, data = x_test.lab)
threshold <- 0.5
predictions_classes <- ifelse(predictions > threshold,1,0)
confusionMatrix(as.factor(predictions_classes), twitch.lab.dtest$isVPN)


```


## Drop no-numeric columns
```{r}
library(glmnet)
library(tidyverse)
twitch.lab.dtrain <- twitch.lab.dtrain[, !(names(twitch.lab.dtrain) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.res.dtrain <- twitch.res.dtrain[, !(names(twitch.res.dtrain) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.lab.dtrain
twitch.res.dtrain

twitch.lab.dtest <- twitch.lab.dtest[, !(names(twitch.lab.dtest) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.res.dtest <- twitch.res.dtest[, !(names(twitch.res.dtest) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.lab.dtest
twitch.res.dtest

```

## Models - LASSO - Lab
```{r}
#perform k-fold cross-validation to find optimal lambda value
lambdas_to_try <- 10^seq(-3, 5, length.out = 100)
x.lab = as.matrix(twitch.lab.dtrain[-80])

cv_model.lab <- cv.glmnet(x.lab, twitch.lab.dtrain$isVPN, alpha = 1,
                      lambda = lambdas_to_try,
                      standardize = TRUE,
                      nfolds = 10,
                      family = "binomial")

#find optimal lambda value that minimizes test MSE
best_lambda.lab <- cv_model.lab$lambda.min
best_lambda.lab

#produce plot of test MSE by lambda value
plot(cv_model.lab) 

cv_best_model.lab <- glmnet(x.lab, twitch.lab.dtrain$isVPN, alpha = 1,
                      lambda = best_lambda.lab,
                      standardize = TRUE,
                      family = "binomial")

```

## Models - LASSO - Res
```{r}
#perform k-fold cross-validation to find optimal lambda value
lambdas_to_try <- 10^seq(-3, 5, length.out = 100)
x.res = as.matrix(twitch.res.dtrain[-80])

cv_model.res <- cv.glmnet(x.res, twitch.res.dtrain$isVPN, alpha = 1,
                      lambda = lambdas_to_try,
                      standardize = TRUE,
                      nfolds = 10,
                      family = "binomial")

#find optimal lambda value that minimizes test MSE
best_lambda.res <- cv_model.res$lambda.min
best_lambda.res

#produce plot of test MSE by lambda value
plot(cv_model.res) 

cv_best_model.res <- glmnet(x.res, twitch.res.dtrain$isVPN, alpha = 1,
                      lambda = best_lambda.lab,
                      standardize = TRUE,
                      family = "binomial")


```

## Validation - LASSO - Lab
```{r}
dtest.lab <- as.matrix(twitch.lab.dtest[-80])
ncol(dtest.lab)
dtest.res <- as.matrix(twitch.res.dtest[-80])
threshold <- 0.5


predictions.lab.lab.lasso <- predict(cv_best_model.lab, s = best_lambda.lab, dtest.lab, type = "response")
predictions.lab.res.lasso <- predict(cv_best_model.lab, s = best_lambda.res, dtest.res, type = "response")
predicted_classes.lab.lab <- ifelse(predictions.lab.lab.lasso > threshold,1,0)
predicted_classes.lab.res <- ifelse(predictions.lab.res.lasso > threshold,1,0)

confmtx.lab.lab.lasso <- confusionMatrix(table(predicted_classes.lab.lab,twitch.lab.dtest$isVPN))
confmtx.lab.res.lasso <- confusionMatrix(table(predicted_classes.lab.res,twitch.res.dtest$isVPN))

print("lab")
confmtx.lab.lab.lasso$byClass
confmtx.lab.lab.lasso$overall

print("res")
confmtx.lab.res.lasso$byClass
confmtx.lab.res.lasso$overall

```


## Validation - LASSO - Res
```{r}
predictions.res.lab.lasso <- predict(cv_best_model.res, s = best_lambda.lab, dtest.lab, type = "response")
predictions.res.res.lasso <- predict(cv_best_model.res, s = best_lambda.res, dtest.res, type = "response")
predicted_classes.res.lab <- ifelse(predictions.res.lab.lasso > threshold,1,0)
predicted_classes.res.res <- ifelse(predictions.res.res.lasso > threshold,1,0)

confmtx.res.lab.lasso <- confusionMatrix(table(predicted_classes.res.lab,twitch.lab.dtest$isVPN))
confmtx.res.res.lasso <- confusionMatrix(table(predicted_classes.res.res,twitch.res.dtest$isVPN))

print("lab")
confmtx.res.lab.lasso$byClass
confmtx.res.lab.lasso$overall

print("res")
confmtx.res.res.lasso$byClass
confmtx.res.res.lasso$overall

```


## export
```{r} 
write.csv(twitch.lab.dtrain, "t2/streaming/dtrain_lab.csv",row.names=FALSE)
write.csv(twitch.res.dtrain, "t2/streaming/dtrain_res.csv",row.names=FALSE)

write.csv(twitch.lab.dtest, "t2/streaming/dtest_lab.csv",row.names=FALSE)
write.csv(twitch.res.dtest, "t2/streaming/dtest_res.csv",row.names=FALSE)

twitch.lab.data <- twitch.lab.data[, !(names(twitch.lab.data) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.res.data <- twitch.res.data[, !(names(twitch.res.data) %in% c("X.dir", "ipOptCpCl_Num"))]

write.csv(twitch.lab.data, "t2/streaming/data_lab.csv",row.names=FALSE)
write.csv(twitch.res.data, "t2/streaming/data_res.csv",row.names=FALSE)

```


```{r}
twitch.lab.1111 <- twitch.lab.1111[, !(names(twitch.lab.1111) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.res.1111 <- twitch.res.1111[, !(names(twitch.res.1111) %in% c("X.dir", "ipOptCpCl_Num"))]
twitch.lab.1111

twitch.lab.1111 <- twitch.lab.1111[-80]
twitch.lab.1111$isLab <- 1
twitch.lab.1111$isLab <- as.factor(twitch.lab.1111$isLab)
twitch.res.1111 <-twitch.res.1111[-80]
twitch.res.1111$isLab <- 0
twitch.res.1111$isLab <- as.factor(twitch.res.1111$isLab)

twitch.lab.1111.trnRows  <- sample(nrow(twitch.lab.1111),nrow(twitch.lab.1111)*0.7)
twitch.lab.1111.dtrain <- twitch.lab.1111[twitch.lab.1111.trnRows,]
twitch.lab.1111.dtest  <- twitch.lab.1111[-twitch.lab.1111.trnRows,]

twitch.res.1111.trnRows  <- sample(nrow(twitch.res.1111),nrow(twitch.res.1111)*0.7)
twitch.res.1111.dtrain <- twitch.res.1111[twitch.res.1111.trnRows,]
twitch.res.1111.dtest  <- twitch.res.1111[-twitch.res.1111.trnRows,]

twitch.1111.dtrain <- rbind(twitch.lab.1111.dtrain,twitch.res.1111.dtrain)
twitch.1111.dtest <- rbind(twitch.lab.1111.dtest,twitch.res.1111.dtest)
ncol(twitch.1111.dtrain)
```

## C45
```{r}
train_control<- trainControl(method="cv", number=10)
twitch.lab.C45Model.locat <- train(isLab ~., method="J48", data=twitch.1111.dtrain,
                tuneLength = 5,
                trControl = train_control)
```

```{r}
twitch.lab.C45Model.locat$finalModel

predictions.c45.locat = predict(twitch.lab.C45Model.locat, newdata = twitch.1111.dtest)
confMatrixes.c45.locat <- confusionMatrix(predictions.c45.locat, twitch.1111.dtest$isLab)
eva.twitch.c45.locat <- confMatrixes.c45.locat$byClass

eva.twitch.c45.locat
confMatrixes.c45.locat$overall
```


## RF
```{r}
# Fitting Random Forest to the train dataset
set.seed(1003)  # Setting seed
twitch.1111.dtrain
repeat_cv <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

twitch.locat.classifier_RF = randomForest(x = twitch.1111.dtrain[-80],
                               y = twitch.1111.dtrain$isLab,
                               ntree = 500,
                               trControl = repeat_cv)

# Importance plot
importance(twitch.locat.classifier_RF)
  
# Variable importance plot
varImpPlot(twitch.locat.classifier_RF)

```



```{r}
predictions.rf.locat = predict(twitch.locat.classifier_RF, newdata = twitch.1111.dtest)
confMatrixes.rf.locat <- confusionMatrix(predictions.rf.locat, twitch.1111.dtest$isLab)
eva.twitch.rf.locat <- confMatrixes.rf.locat$byClass

eva.twitch.rf.locat
confMatrixes.rf.locat$overall

```


# LASSO
```{r}
#perform k-fold cross-validation to find optimal lambda value
lambdas_to_try <- 10^seq(-3, 5, length.out = 100)
x = as.matrix(twitch.1111.dtrain[-80])


cv_model <- cv.glmnet(x, twitch.1111.dtrain$isLab, alpha = 1,
                      lambda = lambdas_to_try,
                      standardize = TRUE,
                      nfolds = 10,
                      family = "binomial")

#find optimal lambda value that minimizes test MSE
best_lambda <- cv_model$lambda.min
best_lambda

#produce plot of test MSE by lambda value
plot(cv_model) 

cv_best_model <- glmnet(x, twitch.1111.dtrain$isLab, alpha = 1,
                      lambda = best_lambda,
                      standardize = TRUE,
                      family = "binomial")


```


```{r}
dtest <- as.matrix(twitch.1111.dtest[-80])
threshold <- 0.5

predictions.locat.lasso <- predict(cv_best_model, s = best_lambda, dtest, type = "response")
predicted_classes.locat.lasso <- ifelse(predictions.locat.lasso > threshold,0,1)

confmtx.locat.lasso <- confusionMatrix(table(predicted_classes.locat.lasso,as.matrix(twitch.1111.dtest$isLab)))

confmtx.locat.lasso$byClass
confmtx.locat.lasso$overall

```


```{r}
write.csv(twitch.1111.dtrain, "t2/streaming/locat_train.csv",row.names=FALSE)
write.csv(twitch.1111.dtest, "t2/streaming/locat_test.csv",row.names=FALSE)

```

